---
title: "sales_summary.R Documentation"
author: "Ross"
date: "2026-10-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

The `sales_summary.R` script demonstrates a simple sales calculation using Base R. It stores five fictional sales values, calculates the total sales using `sum()`, calculates the average sales using `mean()`, and displays both results.

## Inputs

The script uses five fictional sales values entered directly in the code. It does not require external data files or user input.

```{r}
sales <- c(120, 150, 135, 160, 145)
```

## Calculations

The total sales value is calculated using `sum()`, and the average sales value is calculated using `mean()`.

```{r}
total_sales <- sum(sales)
average_sales <- mean(sales)
```

## Outputs

The script displays the calculated total sales and average sales values.

```{r}
total_sales
average_sales
```

The output objects are:

- `total_sales` - the sum of the five sales values.
- `average_sales` - the mean of the five sales values.

## Dependencies

The script uses Base R only. No external R packages or data files are required.